A Data-Driven Framework for Neural Field Modelling

### 2010-11-01 ltx/first_order_framework/LaTeX_Manuscript.tex
changed the table of estimated paprameters

\begin{table}[!ht]
\caption{
\bf{Estimation Results}}
\begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2.5cm}|p{1.5cm}|}

\hline
Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
\hline
$\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
$\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
$\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
$\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
\hline
\end{tabular}
\begin{flushleft}Actual parameter values compared to mean parameter estimates obtained from the 100 Monte Carlo simulations.
\end{flushleft}
\label{tab:Parameters estimates}
\end{table}

>>>>

% \begin{table}[!ht]
% \centering
% \caption{\bf{Estimation Results}}
% % \begin{tabular}{|p{1.5cm}|p{1.5cm}|p{2.5cm}|p{1.5cm}|}
% \begin{tabular}{|c|c|c|c|}	
% \hline
% Parameter & Actual Value & Mean Estimate $\pm$ Std. Dev. & Bias (\%) \\
% \hline
% % $\xi$ & $0.9$ & $0.925\pm 0.004$ & $2.778$ \\
% $\theta_0$ & $10$ & $10.228\pm2.794$ & $2.28$\\
% $\theta_1$ & $-8$ & $-8.495\pm1.913$ & $-6.187$\\
% $\theta_2$ & $0.5$ & $0.545\pm0.077$ & $9$\\
% \hline
% \end{tabular}
% \begin{flushleft}Actual parameter values compared to mean parameter estimates obtained from the 100 Monte Carlo simulations.
% \end{flushleft}
% \label{tab:Parameters estimates}
% \end{table}

% \tiny{\begin{tabular}{lllllllllllllllllll}
% \hline
% & \multicolumn{6}{c|}{$\theta_0$}&\multicolumn{6}{c|}{$\theta_1$}&\multicolumn{6}{c|}{$\theta_2$}\\
% \cline{2-19}
%  &I&II&III&IV&V&VI&I&II&III&IV&V&VI&I&II&III&IV&V&VI\\
% \hline\hline
% Actual Value&$90$&$100$&$110$&$15$&$30$&$50$&$-80$&$-80$&$-80$&$0$&$0$&$0$&$5$&$5$&$5$&$0$&$0$&$0$\\
% Mean Estimate&$103.86$&$101.75$&$98.9$&$35.67$&$40.43$&$61.43$&$-89.05$&$-81.00$&$-73.13$&$-18.16$&$-12.01$&$-15.03$&$5.23$&$4.75$&$4.37$&$0.81$&$0.35$&$0.27$\\
% Std. Dev.&$23.14$&$21.29$&$16.57$&$14.82$&$0.73$&$0.65$\\
% Bias (\%) &at her&\textbf{aici}& & \\
% \hline
% \end{tabular}}

\small{\begin{tabular}{lccccccccc}
Experiment&\multicolumn{3}{c}{I}&\multicolumn{3}{c}{II}&\multicolumn{3}{c}{III}\\
 Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
\hline\hline
Actual Value&$90$&$-80$&$5$&$100$&$-80$&$5$&$110$&$-80$&$5$\\
Mean Estimate&$103.86$&$-89.05$&$5.23$&$101.75$&$-81.00$&$4.76$&$98.90 $&$-73.13$&$4.37$\\
Std. Dev.&$23.14$&$16.57$&$0.74$&$21.30$&$14.82$&$0.65$&$16.48$& $11.72$&$0.54$\\
Bias (\%)& $15.4$&$11.31$&$4.6$&$1.75$&$1.25$&$4.8$&$10.1$&$ 8.58$&$12.6$  \\
\end{tabular}}

\small{\begin{tabular}{lccccccccc}
Experiment&\multicolumn{3}{c}{IV}&\multicolumn{3}{c}{V}&\multicolumn{3}{c}{VI}\\
 Parameters&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$&$\theta_0$&$\theta_1$&$\theta_2$\\
\hline\hline
Actual Value&$15$&$0$&$0$&$30$&$0$&$0$&$50$&$0$&$0$\\
Mean Estimate&$35.68$&$-18.16$&$0.81$&$40.43$&$-12.01$&$ 0.35$&$61.46$&$-15.03$&$0.27$\\
Std. Dev.&$16.72$&$11.77$&$0.53$&$11.47$&$7.8$&$0.36$&$11.51$&$7.56$&$0.29$\\
Bias (\%)&$22.97$&$22.7$&$16.2$&$10.43$&$15.01$&$7$&$0.42$&$18.78$&$5.4$\\
\end{tabular}}
